lab_notebook

### 2018-11-09 lab_notebook.Rmd
- merged projection data and itq - fun graphs - trying to figure out how to update itq/projection with RAMS

#RAM data wrangling
```{r}

ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

ITQ_projection_year <- ITQ_projection %>%
  unite(Name_Year, "CommName", "Year", sep = "-")

@@

>>>>

@@

#Graphs for fun

ABARES_BGRDRSE
implemented ITQs in 1992
```{r}

ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")

graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
  geom_line(size=1)+
  ggtitle("ABARES_BGRDRSE (Australia")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total biomass")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  geom_vline(xintercept = 1992)+
  theme(legend.title=element_blank())

ggplotly(graph_ABARES_BGRDRSE)

#figure out an if then statement for line?

ADFG-HERRTOGE
never implemented ITQs
```{r}
ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")

graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
  geom_line(size=1)+
  ggtitle("ADFG-HERRTOGE (USA)")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total biomass")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

ggplotly(graph_ADFG_HERRTOGE)

#figure out an if then statement for line?
```

#RAM data wrangling
```{r}
ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

ITQ_projection_year <- ITQ_projection %>%
  unite(Name_Year, "CommName", "Year", sep = "-")
```

#Attemps at merging ITQ_projection with rams
Playing with Data

```{r}

IdOrig <- unique(ITQ_projection$IdOrig)
IdOrig
#337 species total

ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")

IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
IdOrig_implemented
#115 species with ITQ implemented

#Total number of species with stocks
#Number of stocks with ITQs implemented
```{r}
IdOrig <- unique(ITQ_projection$IdOrig)
IdOrig
#337 species total

ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")

IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
IdOrig_implemented
#115 species with ITQ implemented
```

Attemts at updating ITQ_projection with Rams
```{r}

##this doesn't work
RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
